
## Journal publications 

* W. Hernandez, K. Tylinski, B. Kultys, A. P. Moore,  E. Nemsic,  N. Roche, J. Shangguan, N Vagdama, H. Treiblmaier,  “Trends and Trajectories for Sustainable Systems: Evolution of Distributed Ledger Taxonomies”, IEEE Access (2025), forthcoming

* Hoadley D., Bartolo M., Chesterman R., Faus A., Hernandez W., Kultys B., Moore A. P., Nemsic E., Roche N., Shangguan J., Steer B., Tylinski K., West N. “A Global Community of Courts? Modelling the Use of Persuasive Authority as a Complex Network”, Frontiers in Physics (2021), 9, p.331 

## Conference publications 

* Y. Lu, M. Bartolo, A. P. Moore, S. Riedel, and P. Stenetorp. “Fantastically ordered prompts and where to find them: Overcoming few-shot prompt order sensitivity”, 2021, ACL 2022 (\textbf{Outstanding Paper Award})

* M. Bartolo, K. Tylinski and A. P. Moore, “Pre-trained Contextual Embeddings for Litigation Code Classification”, 2019 1st International Workshop on AI and Intelligent Assistance for Legal Professionals in the Digital Workplace

* A. P. Moore, S. J. D. Prince and J. Warrell, “Lattice Cut - Constructing superpixels using layer constraints”, IEEE Computer Vision and Pattern Recognition, CVPR 2010. Acceptance Rate: 26.8% 

* J Warrell, Simon J D Prince, A P Moore, Epitomized priors for multi-labeling problems 
IEEE International Conference of Computer Vision, 2812-2819

* J Warrell, A. P. Moore, S Prince, Vistas: Hierarchial boundary priors using multiscale conditional random fields. BMVC 2009, 1-11

* A. P. Moore, S. J. D. Prince, J. Warrell, U. Mohammed and G. Jones, “Scene Shape Priors for Superpixel Segmentation”, IEEE International Conference of Computer Vision, ICCV 2009. Acceptance Rate: 19.6% 

* A. P. Moore, S. J. D. Prince, J. Warrell, U. Mohammed and G. Jones, [Superpixel Lattices](https://ieeexplore.ieee.org/abstract/document/4587471), In IEEE Computer Vision and Pattern Recognition, CVPR 2008. Acceptance Rate: 31.9\% [pdf]()


## Pre-prints 

* Bartolo M., Hoadley D., Hernandez W., Kultys B., Moore A. P., Nemsic E., Roche N., Shangguan J., Tylinski K., P. Stenetorp, “VALUE: Towards Application-driven Benchmarking for Natural Language Processing” (2021), forthcoming


## Book chapters 

* Anil R. Doshi, A. P. Moore, "Toward a Human-AI Task Tensor: A Taxonomy for Organizing Work in the Age of Generative AI" [Axiv](https://arxiv.org/abs/2503.15490) 

* C. Kerrigan and T. Hawitt, “AI Law and Regulation”, 1st ed. 2021, Book Chapter: Real Estate, A. P. Moore, C. Giannoni, N. Kirby and N. Doffman

* A P Moore,  N Roche and N Vagdama, Real Estate and the Internet of Value. Chapter 7. Enabling the Internet of Value : How Blockchain Connects Global Businesses Future of Business and Finance”, Tasca, P. Vadgama, N. Xu, J. 1st ed. 2021.

* N Roche and A P Moore, Oracles and Internet of Things in the Internet of Value. Chapter 14. Enabling the Internet of Value : How Blockchain Connects Global Businesses Future of Business and Finance”, Tasca, P. Vadgama, N. Xu, J. 1st ed. 2021.

## White papers 

* N. Roche, W. Hernandez, T. Grogan, D. Hoadley, A. P. Moore, “Responsive Legal Agreements using Oracles” [UCL CBT Working paper series, 2021](http://blockchain.cs.ucl.ac.uk/wp-content/uploads/2020/07/UCLCBT_DiscussionPaper_Q22020_V2.pdf)

* [Towards a distributed ledger of residential title deeds in the UK - HM Land Registry – Mishcon Working paper series, 2020](https://www.mishcon.com/upload/files/HMLR%20White%20Paper.pdf)

## Online talks and slides 

* [Maps as models - Wardley Maps BarCamp 2020](https://www.youtube.com/watch?v=7-5IGTfiujY)
* [Future Data Scientists: Who are They? - EGG UK 2018](https://videos.dataiku.com/watch/NR8tte6TqskiVrwuvENTLS?)
* [CognitionX hosted Hermann Hauser talk 2016](https://www.youtube.com/watch?v=G3Vh7rY5cik)
* [London-based startup tackles short-term commercial real estate rentals 2013](https://venturebeat.com/2013/03/13/london-based-startup-tackles-short-term-commercial-real-estate-rentals/)

## Media 

